\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-30 document/XSGRB_sample.tex

\newcommand{\griz}{$g' r' i' z'$}
\newcommand{\JHK}{$JHK_{\rm{s}}$}
\newcommand{\gK}{$g' r' i' z' JHK_{\rm{s}}$}
\newcommand{\Msun}{$M_\odot$}
\newcommand{\lya}{Ly$\alpha$} 
\newcommand{\lyb}{Ly$\beta$} 
\newcommand{\hb}{H$\beta$} 
\newcommand{\ha}{H$\alpha$}

\newcommand{\hi}{\ion{H}{1}} 
\newcommand{\hei}{[\ion{He}{1}]} 
\newcommand{\oi}{[\ion{O}{1}]} 
\newcommand{\sii}{[\ion{S}{2}]} 
\newcommand{\siii}{[\ion{S}{3}]} 
\newcommand{\oii}{[\ion{O}{2}]$\lambda$3727} 
\newcommand{\oiii}{[\ion{O}{3}]$\lambda$5007}
\newcommand{\nii}{[\ion{N}{2}]} 
\newcommand{\neiii}{[\ion{Ne}{3}]} 
\newcommand{\feii}{\ion{Fe}{2}} 
\newcommand{\civ}{\ion{C}{4}} 
\newcommand{\cii}{\ion{C}{2}}
\newcommand{\mgi}{\ion{Mg}{1}} 
\newcommand{\mgii}{\ion{Mg}{2}} 
\newcommand{\ali}{\ion{Al}{1}} 
\newcommand{\alii}{\ion{Al}{2}} 
\newcommand{\aliii}{\ion{Al}{3}} 
\newcommand{\SIii}{\ion{Si}{2}} 
\newcommand{\znii}{\ion{Zn}{2}} 
\newcommand{\crii}{\ion{Cr}{2}} 
\newcommand{\mnii}{\ion{Mn}{2}} 
\newcommand{\tiii}{\ion{Ti}{2}} 
\newcommand{\caii}{\ion{Ca}{2}}

@@

>>>>

\newcommand{\griz}{$g' r' i' z'$}
\newcommand{\JHK}{$JHK_{\rm{s}}$}
\newcommand{\gK}{$g' r' i' z' JHK_{\rm{s}}$}
\newcommand{\Msun}{$M_\odot$}
\newcommand{\lya}{Ly$\alpha$} 
\newcommand{\lyb}{Ly$\beta$} 
\newcommand{\hb}{H$\beta$} 
\newcommand{\ha}{H$\alpha$} 
\newcommand{\hg}{H$\gamma$} 
\newcommand{\hi}{\ion{H}{1}} 
\newcommand{\hei}{[\ion{He}{1}]} 
\newcommand{\oi}{[\ion{O}{1}]} 
\newcommand{\sii}{[\ion{S}{2}]} 
\newcommand{\siii}{[\ion{S}{3}]} 
\newcommand{\oii}{[\ion{O}{2}]$\lambda$3727} 
\newcommand{\oiii}{[\ion{O}{3}]$\lambda$5007}
\newcommand{\nii}{[\ion{N}{2}]} 
\newcommand{\neiii}{[\ion{Ne}{3}]} 
\newcommand{\feii}{\ion{Fe}{2}} 
\newcommand{\civ}{\ion{C}{4}} 
\newcommand{\cii}{\ion{C}{2}}
\newcommand{\mgi}{\ion{Mg}{1}} 
\newcommand{\mgii}{\ion{Mg}{2}} 
\newcommand{\ali}{\ion{Al}{1}} 
\newcommand{\alii}{\ion{Al}{2}} 
\newcommand{\aliii}{\ion{Al}{3}} 
\newcommand{\SIii}{\ion{Si}{2}} 
\newcommand{\znii}{\ion{Zn}{2}} 
\newcommand{\crii}{\ion{Cr}{2}} 
\newcommand{\mnii}{\ion{Mn}{2}} 
\newcommand{\tiii}{\ion{Ti}{2}} 
\newcommand{\caii}{\ion{Ca}{2}}

@@

	\subsection{GRB160804A (z = 0.736)}
	The data presented here also formed the basis of GCN \#
	19773\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/19773.gcn3}} and is not
	published elsewhere. Observations started 22.37 hours after the BAT trigger and
	lasted for 2.4ks. The afterglow continuum is detected across the entire
	spectral coverage of X-shooter and absorption lines from \mgi, \mgii, \feii and
	\alii~are found at $z = 0.736$. At the same redshift, emission lines from \oii,
	\oiii, \ha, \hb, \hg, \nii, \sii, \siii are found. A second epoch, lasting
	3.6ks, is obtained after the afterglow has faded, confirming the emission line
	detections.
